Verifying Demonstrations

### 2018-02-28 paper/protocol.tex
Starts rewrite of protocol section

>>>>

\NewCryptoScheme{\PRIVOscheme}{PRIVO}
\NewAlgorithm{\PRIVOsetup}{\PRIVOscheme.\!Setup}
\NewAlgorithm{\PRIVOjoin}{\PRIVOscheme.\!Join}
\NewAlgorithm{\PRIVOparticipate}{\PRIVOscheme.\!Participate}
\NewAlgorithm{\PRIVOsubmit}{\PRIVOscheme.\!Submit}

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
The protocol consists of four phases: the setup, join, participation and 
submission phases.
We have an identification authority \(\ID\), an organizer Oscar, \(\O\), a 
protester Alice (\(\A\)) and a witness Bob \(\B\).

\NewCryptoEntity{\ID}{ID}

\emph{Setup.}
During the setup phase, we set up the needed keys.
